Title

### 2017-04-10 paper.tex
Fix typo

    Based on the works presented above, we have methods to measure the overall wake-up latency and context-switch
    latency, using cyclictest and lmbench. Also, it's able to show that the CFS algorithm has O(1) complexity on
    selecting next task, giving static latency. Thus, overall  and parts of latency of a Linux system can be determined,
    but the measurement methodology and tool of scheduler latency, shown in figure \ref{fig:latency_timeline}, are
    lacking. Therefore, we developed a evaluation tool of scheduler duration jitter, based on methodology method of A
    Decade of Wasted Cores \cite{Lozi:2016:LSD:2901318.2901326}. This methodology method enabled us to record the
    scheduler states including, executing process ID (PID), PID in scheduler run-queue, context switch points, timer
    interrupt execution, scheduling events, etc. on per processor core basis. This methodology method differs from
    profiling based methodology tools, e.g. perf \cite{perf}, lacking high fidelity, all-recorded profiling result of
    the target system. Our proposed tool can do full-detailed record in microsecond scale on x86-64 and ARM system,
    which is able to capture the impact to real-time performance of occasional short-burst scheduler events, which only
    last less that 10us. These events are mostly not shown in the result of sampling based measurement which focus on
    average-case execution time(ACET). By analyzing full-detailed record, we are able to not only capture the worst-case
    execution time (WCET), but also understand the cause of these incidents.

@@

    In aid of these developed tools and work presented above, we did multiple experiments and measurement of 2 ARM
    Cortex-A9 based platform, shown in table I. These platforms are selected as CMP based ARM system are emerging and
    being used in a wide field of applications. These systems are running buildroot \cite{buildroot} built Linux with
    kernel version 4.4 and PR\textunderscore RT \cite{preemptrt} patches.

>>>>

    Based on the works presented above, we have methods to measure the overall wake-up latency and context-switch
    latency, using cyclictest and lmbench. Also, it's able to show that the CFS algorithm has O(1) complexity on
    selecting next task, giving static latency. Thus, overall  and parts of latency of a Linux system can be determined,
    but the measurement methodology and tool of scheduler latency, shown in figure \ref{fig:latency_timeline}, are
    lacking. Therefore, we developed a evaluation tool of scheduler duration jitter, based on methodology method of A
    Decade of Wasted Cores \cite{Lozi:2016:LSD:2901318.2901326}. This methodology method enabled us to record the
    scheduler states including, executing process ID (PID), PID in scheduler run-queue, context switch points, timer
    interrupt execution, scheduling events, etc. on per processor core basis. This methodology method differs from
    profiling based methodology tools, e.g. perf \cite{perf}, lacking of high fidelity, all-recorded profiling result of
    the target system. Our proposed tool can do full-detailed record in microsecond scale on x86-64 and ARM system,
    which is able to capture the impact to real-time performance of occasional short-burst scheduler events, which only
    last less that 10us. These events are mostly not shown in the result of sampling based measurement which focus on
    average-case execution time(ACET). By analyzing full-detailed record, we are able to not only capture the worst-case
    execution time (WCET), but also understand the cause of these incidents.

@@

    In aid of these developed tools and work presented above, we did multiple experiments and measurement of 2 ARM
    Cortex-A9 based platform, shown in table I. These platforms are selected as CMP based ARM system are emerging and
    being used in a wide field of applications. These systems are running buildroot \cite{buildroot} built Linux with
    kernel version 4.4 and PREEMPT\textunderscore RT \cite{preemptrt} patches.
